---
title: "Session 1: Rmarkdown"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: spacelab
---

```{r, setup, include=FALSE}
## This code chunk establishes report options such as suppressing warning messages when executing code and establishing the default size for figures/plots/tables

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      error = TRUE,
                      fig.width = 10, 
                      fig.height = 6
                      ) 

```

```{r, source_data, include = FALSE}
#source(here::here("scripts", "utilities.R"))
#source(here::here("scripts", "functions.R"))
#source(here::here("scripts", "get_data.R"))
#source(here::here("scripts", "process_data.R"))
```

## About this report

This report is intended to be an example of how to build an Rmarkdown report. It will explore different options and features of Rmarkdown.


* This report was last run on `r today()`  

* It contains air quality data from as recent as `r max(airquality[["Month"]])` *(Month)*

* It contains `r nrow(airquality)` records.

</br>

### Tables


#### Static Table

```{r, include = TRUE}
iris %>% 
  tabyl(Species)
```


### Custom Table
```{r, include = TRUE}
iris %>% 
  my_table(Species)
```

</br>

#### Dynamic Table
```{r, include = TRUE}
 iris %>% 
  select(Species, Sepal.Length, Sepal.Width) %>% 
  arrange(desc(Sepal.Length)) %>% 
  DT::datatable(rownames= FALSE)
```

</br>

### Plots

</br>


## APPENDIX

### Resources

* [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/){target - "_blank"}
* [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook){target - "_blank"}
* [Interactive Documents](https://garrettgman.github.io/rmarkdown/authoring_shiny.html#overview){target - "_blank"}
* [R Cheatsheets](https://www.rstudio.com/resources/cheatsheets/){target - "_blank"}
