---
title: "Session 1: Rmarkdown"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: spacelab
---

```{r, setup, include=FALSE}
## This code chunk establishes report options such as suppressing warning messages when executing code and establishing the default size for figures/plots/tables

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      error = TRUE,
                      fig.width = 10, 
                      fig.height = 6
                      ) 

```

```{r, source_data, include = FALSE}
#source(here::here("scripts", "utilities.R"))
#source(here::here("scripts", "functions.R"))
#source(here::here("scripts", "get_data.R"))
#source(here::here("scripts", "process_data.R"))
```

## About this report

This report is intended to be an example of how to build an Rmarkdown report. It will explore different options and features of Rmarkdown.


* This report was last run on `r today()`  

* It contains air quality data from as recent as `r max(airquality[["Month"]])` *(Month)*

* It contains `r nrow(airquality)` records.

</br>

### Tables


#### Static Table

```{r, include = TRUE}
iris %>% 
  janitor::tabyl(Species)
```


### Custom Table
```{r, include = TRUE}
iris %>% 
  my_table(Species)
```

</br>

#### Dynamic Table
```{r, include = TRUE}
 iris %>% 
  select(Species, Sepal.Length, Sepal.Width) %>% 
  arrange(desc(Sepal.Length)) %>% 
  DT::datatable(rownames= FALSE)
```

</br>

### Plots


#### GGPlot2

*Scatter*
```{r, include = TRUE}
scatter <- ggplot(data=iris, aes(x = Sepal.Length, y = Sepal.Width)) 
scatter + geom_point(aes(color=Species, shape=Species)) +
  xlab("Sepal Length") +  ylab("Sepal Width") +
  ggtitle("Sepal Length-Width")
```


*Boxplot*

```{r, include = TRUE}
box <- ggplot(data=iris, aes(x=Species, y=Sepal.Length))
box + geom_boxplot(aes(fill=Species)) + 
  ylab("Sepal Length") + ggtitle("Iris Boxplot") +
  stat_summary(fun.y=mean, geom="point", shape=5, size=4) 
```

*Facets*
```{r, include = TRUE}
facet <- ggplot(data=iris, aes(Sepal.Length, y=Sepal.Width, color=Species)) + 
  geom_point(aes(shape=Species), size=1.5) + geom_smooth(method="lm") +
  xlab("Sepal Length") + ylab("Sepal Width") + ggtitle("Faceting")

# Along rows
facet + facet_grid(. ~ Species)
```

</br>

### Plotly
```{r, include = TRUE}
plot_ly(iris, x=iris$Petal.Length, y=iris$Sepal.Length, 
        mode = "markers", color = iris$Species) %>%
     layout(xaxis=list(title ='Petal Length', range = c(0, 7)), 
            yaxis=list(title ='Sepal.Length', range = c(4, 8)),
            title = 'Graph of Iris Dataset')
```


## APPENDIX

### Resources

* [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/){target="_blank"}
* [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook){target="_blank"}
* [Interactive Documents](https://garrettgman.github.io/rmarkdown/authoring_shiny.html#overview){target="_blank"}
* [Plotly-R](https://plotly-r.com/){target="_blank"}
* [R Cheatsheets](https://www.rstudio.com/resources/cheatsheets/){target="_blank"}
